Structural controllability of ecological networks

### 2018-07-17 paper/manuscript.Rmd
Alternative titles

* Keystoneness, centrality, and the structural controllability of ecological networks

>>>>

* Keystoneness, centrality, and the structural controllability of ecological networks
* Keystone and critical species, a structural controllability perspective of ecological networks
* The controllability of ecological networks
* Species with high control capacity support stable coexistence of pollination communities
* Species with high control capacity support stable coexistence of pollination networks
* A control theory perspective: species with high control capacity support stable coexistence of pollination communities
